An Open Platform for Managing Short Programming Exercises

### 2013-06-22 paper/paper.tex
fixes to pilot study table

\begin{table*}
\centering
\begin{tabular}{llll}
\toprule
Institution & Course & Language & Enrollment\\
\midrule
Canisius College & CS-1 & C/C++ & 30\\
York College & CS-1 & C/C++ & 120\\
Knox College \#1 & CS-1 & Java & 23\\
University of Auckland & Programming for Engineers & C & 30\\
\bottomrule
\end{tabular}
\caption{CloudCoder pilot studies.}
\label{tab:courses}
\end{table*}

>>>>

\begin{table*}
\centering
\begin{tabular}{llll}
\toprule
Institution & Course & Language & Enrollment\\
\midrule
Canisius College & CS-1 & C++ & 30\\
York College & CS-1 & C & 120\\
Knox College & CS-1 & Java & 23\\
University of Auckland & Programming for Engineers & C & 30\\
\bottomrule
\end{tabular}
\caption{CloudCoder pilot studies.}
\label{tab:courses}
\end{table*}
